---
title             : "Et forsøk i artikkelsamarbeid: The moderating effect of papaja"
shorttitle        : "papajatest"

author: 
  - name          : "Julianne K. Sørlie"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Pilestredet, baby"
    email         : "julianneks@me.com"
  - name          : "Henrik Sørlie"
    affiliation   : "2"

affiliation:
  - id            : "1"
    institution   : "Fagerborg skole"
  - id            : "2"
    institution   : "Forsvarets høgskole"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
```

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

Her har vi en artikkel [@annenLongitudinalEffectsOCB2015a]. Dette er en veldig viktig artikkel. I denne artikkelen skal vi vise at ... spennende funn [@fosseActivePassiveForms2019a]. Veldig spennende. Dette har implikasjoner for teori og praksis.

Her kommer det enda mer greier i innledningen. For eksempel er det spesielt relevant at tidligere studier viser at...

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

```{r}
# Her kommer det noen analyser

resultat <- 2 + 2

```

Resultatet av analysene var at `r printnum(resultat)` var riktige.

# Results

# Discussion
Ok, da var  det på tide med diskusjonen da. Og det er jo så mye å diskutere [@cerasoliPerformanceIncentivesNeeds2016; @christianWorkEngagementQuantitative2011]. F.eks. vil jeg gjerne påpeke at denne diskusjonen diskuterer mange temaer som er verdt å diskutere [@langfredEffectsTaskAutonomy2004]. Så da tenker jeg vi legger den død [@demeroutiProductiveCounterproductiveJob2015]. 

\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
